Generalised Management Strategy Evaluation: modelling biodiversity and food security

### 2019-01-05 notebook/presentation/GMSE_presentation.Rmd
Stable first draft

- Maximise land yield
- Maximise resource use

@@

## Social conflict and management

Results

@@

## Future work PhD

@@

@@

**General idea of the paper**

- Detail 1
- Detail 2
- Detail 3

@@

## Future work ML

Where next version will go

## Summary and links

@@

>>>>

- Maximise resource use
- Maximise land yield

@@

![](gmse_power4.png)

@@

## Using AI in population management

@@

![](IAPETUS.png)

@@

**Using artificial intelligence to improve decision-making in conservation conflict**

- Develop a framework for modelling AI for stake-holder decision-making
- Develop AI software to simulate stake-holder interaction and negotiation
- Apply agent-based decision-making to one or more case studies to predict long-term population dynamics

@@

## AI of stake-holder decision-making

![](game_to_AI.png)

@@

# Supporting Information: Genetic algorithm

<!--- 
    START OF THE GENETIC ALGORITHM SET OF SLIDES  ------------------------------
--->

## Structure of a genetic algorithm

```{r, echo=FALSE}
library(gamesGA);
mbox <- function(x0, x1, y0, y1){
    xx <- seq(from=x0, to=x1, length.out = 100);
    yy <- seq(from=y0, to=y1, length.out = 100);
    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
    return(list(x=xd, y=yd));
}
par(mar=c(0,0,0,0));
# ===============================================================
plot(x=0, y=0, type="n", xlim=c(0,200), ylim=c(0,100), xaxt="n", yaxt="n",
     xlab="",ylab="", bty="n");
abox <- mbox(x0 = 0, x1 = 45, y0 = 70, y1 = 90);
polygon(x=abox$x, y=abox$y, lwd=3, border="red", col="rosybrown1");
text(x=22, y=85, labels="Random", col="black");
text(x=22, y=80, labels="seed of", col="black");
text(x=22, y=75, labels="strategies", col="black");
# --------------------------------------------------------------
cbox <- mbox(x0 = 70, x1 = 140, y0 = 0, y1 = 90);
polygon(x=cbox$x, y=cbox$y, lwd=3, border="goldenrod4", col="gold3");
arrows(x0=46, x1=70, y0=82, y1=82, lwd=2, length=0.15);
dbox <- mbox(x0 = 75, x1 = 135, y0 = 75, y1 = 88);
polygon(x=dbox$x, y=dbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=84, labels="Begin new", col="black");
text(x=105, y=79, labels="generation", col="black");
# ===============================================================
```

**Table of strategies**

```{r, echo=FALSE}
randvals <- sample(x=1:5, size=32, replace=TRUE);
agents   <- matrix(data=randvals, nrow=8);
rownames(agents) <- c("Strategy 1", "Strategy 2", "Strategy 3", "Strategy 4",
                      "Strategy 5", "Strategy 6", "Strategy 7", "Strategy 8");
colnames(agents) <- c("L1", "L2", "L3", "L4");
kable(agents, format="html");
```

## Structure of a genetic algorithm

```{r, echo=FALSE}
mbox <- function(x0, x1, y0, y1){
    xx <- seq(from=x0, to=x1, length.out = 100);
    yy <- seq(from=y0, to=y1, length.out = 100);
    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
    return(list(x=xd, y=yd));
}
par(mar=c(0,0,0,0));
# ===============================================================
plot(x=0, y=0, type="n", xlim=c(0,200), ylim=c(0,100), xaxt="n", yaxt="n",
     xlab="",ylab="", bty="n");
abox <- mbox(x0 = 0, x1 = 45, y0 = 70, y1 = 90);
polygon(x=abox$x, y=abox$y, lwd=3, border="red", col="rosybrown1");
text(x=22, y=85, labels="Random", col="black");
text(x=22, y=80, labels="seed of", col="black");
text(x=22, y=75, labels="strategies", col="black");
# --------------------------------------------------------------
cbox <- mbox(x0 = 70, x1 = 140, y0 = 0, y1 = 90);
polygon(x=cbox$x, y=cbox$y, lwd=3, border="goldenrod4", col="gold3");
arrows(x0=46, x1=70, y0=82, y1=82, lwd=2, length=0.15);
dbox <- mbox(x0 = 75, x1 = 135, y0 = 75, y1 = 88);
polygon(x=dbox$x, y=dbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=84, labels="Begin new", col="black");
text(x=105, y=79, labels="generation", col="black");
# --------------------------------------------------------------
ebox <- mbox(x0 = 75, x1 = 135, y0 = 63, y1 = 73);
polygon(x=ebox$x, y=ebox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=68, labels="recombination", col="black");
# ===============================================================
```

**Table of strategies**

```{r, echo=FALSE}
for(i in 1:dim(agents)[1]){
    for(j in 1:dim(agents)[2]){
        check <- runif(n=1);
        if(check < 0.2){
            other            <- sample(x=1:dim(agents)[1], size=1);
            temp             <- agents[i,j];
            agents[i,j]      <- agents[other, j];
            agents[other, j] <- temp;
        }
    }
}
kable(agents, format="html");
```

## Structure of a genetic algorithm

```{r, echo=FALSE}
mbox <- function(x0, x1, y0, y1){
    xx <- seq(from=x0, to=x1, length.out = 100);
    yy <- seq(from=y0, to=y1, length.out = 100);
    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
    return(list(x=xd, y=yd));
}
par(mar=c(0,0,0,0));
# ===============================================================
plot(x=0, y=0, type="n", xlim=c(0,200), ylim=c(0,100), xaxt="n", yaxt="n",
     xlab="",ylab="", bty="n");
abox <- mbox(x0 = 0, x1 = 45, y0 = 70, y1 = 90);
polygon(x=abox$x, y=abox$y, lwd=3, border="red", col="rosybrown1");
text(x=22, y=85, labels="Random", col="black");
text(x=22, y=80, labels="seed of", col="black");
text(x=22, y=75, labels="strategies", col="black");
# --------------------------------------------------------------
cbox <- mbox(x0 = 70, x1 = 140, y0 = 0, y1 = 90);
polygon(x=cbox$x, y=cbox$y, lwd=3, border="goldenrod4", col="gold3");
arrows(x0=46, x1=70, y0=82, y1=82, lwd=2, length=0.15);
dbox <- mbox(x0 = 75, x1 = 135, y0 = 75, y1 = 88);
polygon(x=dbox$x, y=dbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=84, labels="Begin new", col="black");
text(x=105, y=79, labels="generation", col="black");
# --------------------------------------------------------------
ebox <- mbox(x0 = 75, x1 = 135, y0 = 63, y1 = 73);
polygon(x=ebox$x, y=ebox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=68, labels="recombination", col="black");
# --------------------------------------------------------------
fbox <- mbox(x0 = 75, x1 = 135, y0 = 51, y1 = 61);
polygon(x=fbox$x, y=fbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=56, labels="mutation", col="black");
# ===============================================================
```

**Table of strategies**

```{r, echo=FALSE}
for(i in 1:dim(agents)[1]){
    for(j in 1:dim(agents)[2]){
        check <- runif(n=1);
        if(check < 0.2){
            agents[i,j]  <- sample(x=1:5, size=1);
        }
    }
}
kable(agents, format="html");
```

## Structure of a genetic algorithm

```{r, echo=FALSE}
mbox <- function(x0, x1, y0, y1){
    xx <- seq(from=x0, to=x1, length.out = 100);
    yy <- seq(from=y0, to=y1, length.out = 100);
    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
    return(list(x=xd, y=yd));
}
par(mar=c(0,0,0,0));
# ===============================================================
plot(x=0, y=0, type="n", xlim=c(0,200), ylim=c(0,100), xaxt="n", yaxt="n",
     xlab="",ylab="", bty="n");
abox <- mbox(x0 = 0, x1 = 45, y0 = 70, y1 = 90);
polygon(x=abox$x, y=abox$y, lwd=3, border="red", col="rosybrown1");
text(x=22, y=85, labels="Random", col="black");
text(x=22, y=80, labels="seed of", col="black");
text(x=22, y=75, labels="strategies", col="black");
# --------------------------------------------------------------
cbox <- mbox(x0 = 70, x1 = 140, y0 = 0, y1 = 90);
polygon(x=cbox$x, y=cbox$y, lwd=3, border="goldenrod4", col="gold3");
arrows(x0=46, x1=70, y0=82, y1=82, lwd=2, length=0.15);
dbox <- mbox(x0 = 75, x1 = 135, y0 = 75, y1 = 88);
polygon(x=dbox$x, y=dbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=84, labels="Begin new", col="black");
text(x=105, y=79, labels="generation", col="black");
# --------------------------------------------------------------
ebox <- mbox(x0 = 75, x1 = 135, y0 = 63, y1 = 73);
polygon(x=ebox$x, y=ebox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=68, labels="recombination", col="black");
# --------------------------------------------------------------
fbox <- mbox(x0 = 75, x1 = 135, y0 = 51, y1 = 61);
polygon(x=fbox$x, y=fbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=56, labels="mutation", col="black");
# --------------------------------------------------------------
gbox <- mbox(x0 = 75, x1 = 135, y0 = 39, y1 = 49);
polygon(x=gbox$x, y=gbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=44, labels="check fitness", col="black");
# ===============================================================
```

**Table of strategies**

```{r, echo=FALSE}
fit <- apply(agents,1,sum);
kable(cbind(agents,fit), format="html");
```

## Structure of a genetic algorithm

```{r, echo=FALSE}
mbox <- function(x0, x1, y0, y1){
    xx <- seq(from=x0, to=x1, length.out = 100);
    yy <- seq(from=y0, to=y1, length.out = 100);
    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
    return(list(x=xd, y=yd));
}
par(mar=c(0,0,0,0));
# ===============================================================
plot(x=0, y=0, type="n", xlim=c(0,200), ylim=c(0,100), xaxt="n", yaxt="n",
     xlab="",ylab="", bty="n");
abox <- mbox(x0 = 0, x1 = 45, y0 = 70, y1 = 90);
polygon(x=abox$x, y=abox$y, lwd=3, border="red", col="rosybrown1");
text(x=22, y=85, labels="Random", col="black");
text(x=22, y=80, labels="seed of", col="black");
text(x=22, y=75, labels="strategies", col="black");
# --------------------------------------------------------------
cbox <- mbox(x0 = 70, x1 = 140, y0 = 0, y1 = 90);
polygon(x=cbox$x, y=cbox$y, lwd=3, border="goldenrod4", col="gold3");
arrows(x0=46, x1=70, y0=82, y1=82, lwd=2, length=0.15);
dbox <- mbox(x0 = 75, x1 = 135, y0 = 75, y1 = 88);
polygon(x=dbox$x, y=dbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=84, labels="Begin new", col="black");
text(x=105, y=79, labels="generation", col="black");
# --------------------------------------------------------------
ebox <- mbox(x0 = 75, x1 = 135, y0 = 63, y1 = 73);
polygon(x=ebox$x, y=ebox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=68, labels="recombination", col="black");
# --------------------------------------------------------------
fbox <- mbox(x0 = 75, x1 = 135, y0 = 51, y1 = 61);
polygon(x=fbox$x, y=fbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=56, labels="mutation", col="black");
# --------------------------------------------------------------
gbox <- mbox(x0 = 75, x1 = 135, y0 = 39, y1 = 49);
polygon(x=gbox$x, y=gbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=44, labels="check fitness", col="black");
# --------------------------------------------------------------
hbox <- mbox(x0 = 75, x1 = 135, y0 = 27, y1 = 37);
polygon(x=hbox$x, y=hbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=32, labels="selection", col="black");
# ===============================================================
```

**Table of strategies**

```{r, echo=FALSE}
ord <- order(fit, decreasing=TRUE);
agents <- agents[ord,];
fit    <- fit[ord];
kable(cbind(agents,fit), format="html");
```

## Structure of a genetic algorithm

```{r, echo=FALSE}
mbox <- function(x0, x1, y0, y1){
    xx <- seq(from=x0, to=x1, length.out = 100);
    yy <- seq(from=y0, to=y1, length.out = 100);
    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
    return(list(x=xd, y=yd));
}
par(mar=c(0,0,0,0));
# ===============================================================
plot(x=0, y=0, type="n", xlim=c(0,200), ylim=c(0,100), xaxt="n", yaxt="n",
     xlab="",ylab="", bty="n");
abox <- mbox(x0 = 0, x1 = 45, y0 = 70, y1 = 90);
polygon(x=abox$x, y=abox$y, lwd=3, border="red", col="rosybrown1");
text(x=22, y=85, labels="Random", col="black");
text(x=22, y=80, labels="seed of", col="black");
text(x=22, y=75, labels="strategies", col="black");
# --------------------------------------------------------------
cbox <- mbox(x0 = 70, x1 = 140, y0 = 0, y1 = 90);
polygon(x=cbox$x, y=cbox$y, lwd=3, border="goldenrod4", col="gold3");
arrows(x0=46, x1=70, y0=82, y1=82, lwd=2, length=0.15);
dbox <- mbox(x0 = 75, x1 = 135, y0 = 75, y1 = 88);
polygon(x=dbox$x, y=dbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=84, labels="Begin new", col="black");
text(x=105, y=79, labels="generation", col="black");
# --------------------------------------------------------------
ebox <- mbox(x0 = 75, x1 = 135, y0 = 63, y1 = 73);
polygon(x=ebox$x, y=ebox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=68, labels="recombination", col="black");
# --------------------------------------------------------------
fbox <- mbox(x0 = 75, x1 = 135, y0 = 51, y1 = 61);
polygon(x=fbox$x, y=fbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=56, labels="mutation", col="black");
# --------------------------------------------------------------
gbox <- mbox(x0 = 75, x1 = 135, y0 = 39, y1 = 49);
polygon(x=gbox$x, y=gbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=44, labels="check fitness", col="black");
# --------------------------------------------------------------
hbox <- mbox(x0 = 75, x1 = 135, y0 = 27, y1 = 37);
polygon(x=hbox$x, y=hbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=32, labels="selection", col="black");
# --------------------------------------------------------------
ibox <- mbox(x0 = 75, x1 = 135, y0 = 15, y1 = 25);
polygon(x=ibox$x, y=ibox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=20, labels="replacement", col="black");
# ===============================================================
```

**Table of strategies**

```{r, echo=FALSE}
agents <- rbind(agents[1,],
                agents[1,],
                agents[2,],
                agents[2,],
                agents[3,],
                agents[3,],
                agents[4,],
                agents[4,]
                );
fit    <- c(fit[1], fit[1], fit[2], fit[2], fit[3], fit[3], fit[4], fit[4]);
kable(cbind(agents,fit), format="html");
```

## Structure of a genetic algorithm

```{r, echo=FALSE}
mbox <- function(x0, x1, y0, y1){
    xx <- seq(from=x0, to=x1, length.out = 100);
    yy <- seq(from=y0, to=y1, length.out = 100);
    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
    return(list(x=xd, y=yd));
}
par(mar=c(0,0,0,0));
# ===============================================================
plot(x=0, y=0, type="n", xlim=c(0,200), ylim=c(0,100), xaxt="n", yaxt="n",
     xlab="",ylab="", bty="n");
abox <- mbox(x0 = 0, x1 = 45, y0 = 70, y1 = 90);
polygon(x=abox$x, y=abox$y, lwd=3, border="red", col="rosybrown1");
text(x=22, y=85, labels="Random", col="black");
text(x=22, y=80, labels="seed of", col="black");
text(x=22, y=75, labels="strategies", col="black");
# --------------------------------------------------------------
cbox <- mbox(x0 = 70, x1 = 140, y0 = 0, y1 = 90);
polygon(x=cbox$x, y=cbox$y, lwd=3, border="goldenrod4", col="gold3");
arrows(x0=46, x1=70, y0=82, y1=82, lwd=2, length=0.15);
dbox <- mbox(x0 = 75, x1 = 135, y0 = 75, y1 = 88);
polygon(x=dbox$x, y=dbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=84, labels="Begin new", col="black");
text(x=105, y=79, labels="generation", col="black");
# --------------------------------------------------------------
ebox <- mbox(x0 = 75, x1 = 135, y0 = 63, y1 = 73);
polygon(x=ebox$x, y=ebox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=68, labels="recombination", col="black");
# --------------------------------------------------------------
fbox <- mbox(x0 = 75, x1 = 135, y0 = 51, y1 = 61);
polygon(x=fbox$x, y=fbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=56, labels="mutation", col="black");
# --------------------------------------------------------------
gbox <- mbox(x0 = 75, x1 = 135, y0 = 39, y1 = 49);
polygon(x=gbox$x, y=gbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=44, labels="check fitness", col="black");
# --------------------------------------------------------------
hbox <- mbox(x0 = 75, x1 = 135, y0 = 27, y1 = 37);
polygon(x=hbox$x, y=hbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=32, labels="selection", col="black");
# --------------------------------------------------------------
ibox <- mbox(x0 = 75, x1 = 135, y0 = 15, y1 = 25);
polygon(x=ibox$x, y=ibox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=20, labels="replacement", col="black");
# --------------------------------------------------------------
jbox <- mbox(x0 = 75, x1 = 135, y0 = 3, y1 = 13);
polygon(x=jbox$x, y=jbox$y, lwd=3, border="goldenrod4", col="white");
text(x=105, y=8, labels="converge?", col="black");
# --------------------------------------------------------------
bbox <- mbox(x0 = 0, x1 = 45, y0 = 20, y1 = 40);
polygon(x=bbox$x, y=bbox$y, lwd=3, border="blue", col="lightsteelblue1");
arrows(x0=70, x1=22.5, y0=5, y1=5, lwd=2, length=0.0);
arrows(x0=22, x1=22, y0=5, y1=20, lwd=2, length=0.15);
arrows(x0=55, x1=55, y0=5, y1=82, lwd=2, length=0.15);
text(x=15, y=10, labels="Yes", col="black", srt=90);
text(x=50, y=10, labels="No", col="black", srt=90);
text(x=22, y=33, labels="Adaptive", col="black");
text(x=22, y=28, labels="strategies", col="black");
# ===============================================================
```

**Table of strategies**

```{r, echo=FALSE}
kable(cbind(agents,fit), format="html");
```

<!--- 
    END OF THE GENETIC ALGORITHM SET OF SLIDES  --------------------------------
--->

# Example of a genetic algorithm for Prisoner's dilemma

## Iterated Prisoner's dilemma rules {.smaller}

![](payoff_matrix_sm.png)
**General structure of Prisoner's dilemma scenario**

![](pd_pays.png)
**Specific payoffs satisfying a Prisoner's dilemma scenario**

## Use of genetic algorithms {.smaller}

**Each locus is an focal player's choice given an opponent's past three choices (plus one choice of first move)**

<hr>

|                  | **CCC** | **CCD** | **CDC** | **CDD** | **DCC** | **DCD** | **DDC** | **DDD** | **1st** |
|------------------|---------|---------|---------|---------|---------|---------|---------|---------|---------|
| **Strategy 1**   | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  |
| **Strategy 2**   | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  |
| **...**          |   ...   |   ...   |   ...   |   ...   |   ...   |   ...   |   ...   |   ...   |   ...   |
| **Strategy N-1** | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  |
| **Strategy N**   | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  | Choice  |

<hr>

**Total of 512 possible strategies**

## Use of genetic algorithms {.smaller}

```{r, echo=FALSE}
inputPanel(

  numericInput("CC", label = "CC", 0, width="30%"),
  numericInput("DC", label = "DC", 0, width="30%"),
  numericInput("CD", label = "CD", 0, width="30%"),
  numericInput("DD", label = "DD", 0, width="30%"),
  style='width: 2000px; height: 60px'
)
```

```{r, echo=FALSE}
gres <- reactive({ 
     cc <- input$CC;
     dc <- input$DC;
     cd <- input$CD;
     dd <- input$DD;
     rd <- 100;
     gn <- 100;
     co <- 0.05;
     mu <- 0.05;

     game_res <- games_ga(CC = cc, DC = dc, CD = cd, DD = dd, rounds = rd,
                          generations = gn, cross_prob = co, 
                          mutation_prob = mu, num_opponents = 100);     
     all <- c(game_res$genos, "break_1",
              rownames(game_res$genos), "break_2",
              game_res$fitness);
    })
```

```{r, echo = FALSE}
renderPlot({
    break2    <- which(gres()=="break_2")[1]+1;
    end       <- length(gres());
    fitnesses <- gres()[break2:end];
    fitnesses <- as.numeric(fitnesses);
    mean_fit  <- fitnesses / (100 * 100);
    maxpt     <- max(c(input$CC, input$CD, input$DC, input$DD));
    par(mar=c(5,5,1,1));
    plot(x = 1:length(mean_fit), y=mean_fit, type="l", ylim=c(0,maxpt), lwd = 3,
        xlab="Generation", ylab = "Mean strategy fitness per round",
         cex.axis=1.5, cex.lab=1.5);
})
```

## Adaptive strategies simulated {.smaller}

```{r, echo=FALSE}
renderTable({
      break1   <- which(gres()=="break_1")[1] - 1;
      break2   <- which(gres()=="break_2")[1] - 1;
      geno_vec <- gres()[1:break1];
      geno_row <- gres()[(break1+2):break2];
      genos    <- matrix(data =  geno_vec, ncol = 10, byrow = FALSE);
      rownames(genos) <- geno_row;
      colnames(genos) <- c("CCC", "CCD", "CDC", "CDD", "DCC", "DCD", "DDC",
                           "DDD", "1st", "Final %");
      final_table <- genos[1:10,];

}, include.rownames=TRUE)
```
